---
title: ""
---

<br>

### Plotly Examples
* Plotly is one of the many great ways to make interactive visualizations
* I plan to add more, but here are a few to get started
* Each, as you can see, is just a few lines of code
* Nothing too flashy, just examples to see it doesn't take long to learn
* Let's get started, first we'll load the packages and data

```{r, message = FALSE}
library(ggplot2)
library(plotly)
datums <- read.csv("~/Jeff/rSpace/Data/crabDatums1950To2016.csv")
```

<br>

#### Lines
* All these lines are pretty busy and hard to follow
* Plotly solves that problem:
    * Just double click the legend (to the right) to remove them
    * Then click the States you want to see
* Of course you can hover in the visualization for more info
* And more options in the upper right to zoom, pan, download, etc...
* Again, nothing flashy, but not bad for 2 lines of code

```{r, message = FALSE, fig.height = 7, fig.width = 9}
p1 <- ggplot(datums, aes(x = Year, y = PoundsMillion, color = State))
ggplotly(p1 + geom_line())
```

<br>

#### Jitter
* This Jitter Visualization is only mildly useful without interactivity
* With the hover info, it makes a quick way to explore lots of points
* For example, we can quickly see Landings in descending order and which year
* Assuming you're interested in that sort of thing (I am)

```{r, message = FALSE, fig.height = 7, fig.width = 9}
p2 <- ggplot(datums, aes(x = State, y = PoundsMillion))
ggplotly(p2 + geom_point(aes(color = Year),
                         alpha = 0.5, size = 1.5,
                         position = position_jitter(width  = 0.25,
                                                    height = 0)))
```

<br>

#### Area
* I'm thinking you get the idea

```{r, message = FALSE, fig.height = 7, fig.width = 9}
p3 <- ggplot(subset(datums, State %in% c("MD", "LA", "NC","VA")),
             aes(x = Year, y = PoundsMillion, fill = State))
ggplotly(p3 + geom_area())
```

#### Another Jitter
* Again, you get the idea

```{r, message = FALSE, fig.height = 7, fig.width = 9}
p4 <- ggplot(subset(datums,
                    State %in% c("MD", "VA", "NJ", "FL",
                                 "LA", "NC", "SC","TX")),
             aes(x = Region, y = PoundsMillion))
ggplotly(p4 + geom_point(aes(color = State),
                         alpha = 0.5, size = 2,
                         position = position_jitter(width  = 0.25,
                                                    height = 0)))
```



<br>
<br>


